Microlensing as a possible probe of the internal structure of quasars

### 2014-04-15 paper1/ms.tex

\title{Probing internal structure of distant quasars using Microlensing}

\author[TBD] {TBD\thanks{}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,  Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

We present a toy model to parametrize and constraint the innermost environment of a distant quasar using microlensing. 
\end{abstract}

>>>>

\title{Microlensing as a possible probe of the internal structure of quasars}

\author[I. Mohammed et al.] {Irshad Mohammed\thanks{irshad@physik.uzh.ch}$^1$,
Mihai Tomozeiu$^1$, Manuel Rabold$^1$,
\newauthor
Prasenjit Saha,$^1$ and Joachim Wambsgans$^2$\\
$^1${Institute for Theoretical Physics, University of Z$\ddot{u}$rich, 8057 Z$\ddot{u}$rich Switzerland}\\
$^2${University of Heidelberg, Germany}
}

@@

In quasars that have been lensed by galaxies, the point-like images
sometimes show sharp brightness variations (microlensing).  These
brightness changes are associated with the innermost region of the
quasar passing behind a complicated pattern of caustics due to the
stars in the lensing galaxy.  In this paper, we study whether the
universal properties of optical caustics could enable extraction of
shape information about the central engine of quasars.  We present a
toy model with a crescent-shaped source crossing a fold caustic.  The
silhouette of a black hole over an accretion disk tends to produce
roughly crescent sources.  When a crescent source crosses a fold
caustic, the resulting light curve is noticeably different from the
case of a disc or Gaussian source.  The crescent parameters, apart
from one degeneracy, can be recovered.
\end{abstract}
